\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-09-18 manuscript/anon.tex
pdf minor version = 4
fixed image overlap

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width = .9\textwidth]{figures/normal}
  \includegraphics[width = .9\textwidth]{figures/gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ (upper) and marginal gamma distribution with true data
    generating distribution $\Gamma(8,1)$ (lower).}
  \label{fig:qq}
\end{figure}

>>>>

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

@@

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal}
  \centering
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$.}
    \hspace{5cm}
  \includegraphics[width = .9\textwidth]{figures/gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data
    generating distribution $\Gamma(8,1)$.}
  \label{fig:qq}
\end{figure}
